Errata

### 2025-04-06 tex/Manuscript-1.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.

\begin{center}
    \textbf{\Large Manuscript 1}

    \vspace{0.3cm}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}

    \vspace{0.5cm}

    Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Victoria Rodríguez\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4}, Rómulo Oses\textsuperscript{5}, Oscar Seguel\textsuperscript{6}, Dirk Wagner\textsuperscript{3,7}, and Thomas Scholten\textsuperscript{1}

    \vspace{0.2cm}
\end{center}

@@

\vspace{0.5cm}

\begin{center}
    Submitted: March 07, 2022\\
    Accepted: October 22, 2022\\
    Published: December 07, 2022
\end{center}

@@

\bibliographystyle{natbib}
\bibliography{literatur}

>>>>

\begin{center}
    \textbf{\Large Manuscript 1}
\end{center}

\vspace{0.1cm}

\begin{center}
    \textbf{\huge Biocrust-linked changes in soil aggregate stability along a climatic gradient in the Chilean Coastal Range}
\end{center}
\vspace{0.2cm}
\begin{center}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}
\end{center}
    \vspace{0.1cm}
\end{center}
    \begin{justify}

    Nicolás Riveras-Muñoz\textsuperscript{1}, Steffen Seitz\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Victoria Rodríguez\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4}, Rómulo Oses\textsuperscript{5}, Oscar Seguel\textsuperscript{6}, Dirk Wagner\textsuperscript{3,7}, and Thomas Scholten\textsuperscript{1}

    \vspace{0.2cm}
    \end{justify}

@@

\vspace{0.2cm}

\begin{flushleft}
    Submitted: March 07, 2022\\
    Accepted: October 22, 2022\\
    Published: December 07, 2022
\end{flushleft}

@@

\bibliographystyle{natbib} % Consider changing to a style compatible with KOMA/natbib if issues arise
\bibliography{literatur_all_clean}

### 2025-04-06 tex/Manuscript-2.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.

\begin{center}
  \textbf{\Large Manuscript 2}

  \vspace{0.3cm}
  \textit{Geoderma}\\
  \textit{Submitted}

  \vspace{0.5cm}

  Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Corinna Gall\textsuperscript{1}, Victoria Rodríguez\textsuperscript{2}, Kristina Witzgall\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4,5}, Rómulo Oses\textsuperscript{6}, Oscar Seguel\textsuperscript{7}, Dirk Wagner\textsuperscript{2,8}, and Thomas Scholten\textsuperscript{1}

  \vspace{0.2cm}
\end{center}

@@

\vspace{0.5cm}
\begin{center}
  Submitted: March 17, 2025\\
\end{center}
\cleardoublepage

>>>>

\begin{center}
  \textbf{\Large Manuscript 2}
\end{center}

\vspace{0.1cm}

\begin{center}
  \textbf{\huge Biocrusts as climate-dependent regulators of erosion, water and nutrient cycling}
\end{center}

\vspace{0.2cm}

\begin{center}
  \textit{Geoderma}\\
  \textit{Submitted}
\end{center}
\vspace{0.1cm}

\begin{justify}
  Nicolás Riveras-Muñoz\textsuperscript{1}, Steffen Seitz\textsuperscript{1}, Corinna Gall\textsuperscript{1}, Victoria Rodríguez\textsuperscript{2}, Kristina Witzgall\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4,5}, Rómulo Oses\textsuperscript{6}, Oscar Seguel\textsuperscript{7}, Dirk Wagner\textsuperscript{2,8}, and Thomas Scholten\textsuperscript{1}
\end{justify}

\vspace{0.2cm}

@@

\vspace{0.4cm}

\begin{flushleft}
  Submitted: March 17, 2025\\
\end{flushleft}

\cleardoublepage

### 2025-04-06 tex/Manuscript-3.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.

\chapter{Microbial impact on initial soil formation in arid and semiarid environments under simulated climate change}
\label{chap:manuscript3} % Label for potential cross-referencing (start page)

\begin{center}
    \textbf{\Large Manuscript 3}

    \vspace{0.3cm}
    \textit{Frontiers in Microbiology}\\
    \textit{DOI 10.3389/fmicb.2024.1319997}

@@

    Victoria Rodríguez\textsuperscript{1 *}, Alexander Bartholomäus\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Nicolás Riveras-Muñoz\textsuperscript{3}, Romulo Oses\textsuperscript{4}, Susanne Liebner\textsuperscript{1,5}, Jens Kallmeyer\textsuperscript{1}, Oliver Rach\textsuperscript{6}, Carsten W. Mueller\textsuperscript{7,8}, Oscar Seguel\textsuperscript{9}, Thomas Scholten\textsuperscript{3} and Dirk Wagner\textsuperscript{1,10}

    \vspace{0.2cm}
  \end{center}

  \begin{scriptsize}
    \begin{justify}

      \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Potsdam, Germany\\
      \textsuperscript{2}Soil Science, TUM School of Life Sciences, Technical University of Munich, Freising-Weihenstephan, Germany\\
      \textsuperscript{3}Department of Geosciences, Soil Science and Geomorphology, University of T{\"u}bingen, T{\"u}bingen, Germany\\
      \textsuperscript{4}Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama (CRIDESAT), Universidad de Atacama, Copiap{\'o}, Chile\\
      \textsuperscript{5}Institute of Biochemistry and Biology, University of Potsdam, Potsdam, Germany\\
      \textsuperscript{6}GFZ German Research Centre for Geosciences, Section Geomorphology, Potsdam, Germany\\
      \textsuperscript{7}Institute for Ecology, Chair of Soil Science, Technische Universit{\"a}t Berlin, Berlin, Germany\\
      \textsuperscript{8}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark\\
      \textsuperscript{9}Facultad de Ciencias Agron{\'o}micas, Universidad de Chile, Santiago, Chile\\
      \textsuperscript{10}Institute of Geosciences, University of Potsdam, Potsdam, Germany

    \end{justify}
  \end{scriptsize}

  \vspace{0.5cm}
  \begin{center}
    Received: 11 October 2023\\
    Accepted: 02 January 2024\\
    Published: 17 January 2024
  \end{center}
  \cleardoublepage

@@

\bibliographystyle{natbib}
\bibliography{literatur-M3}

>>>>

\chapter{Microbial impact on initial soil formation in arid and semiarid environments under simulated climate change}

\label{chap:manuscript3} % Label for potential cross-referencing (start page)

\begin{center}
  \textbf{\Large Manuscript 3}
\end{center} 
\vspace{0.1cm}
\begin{center}
  \textbf{\huge Microbial impact on initial soil formation in arid and semiarid environments under simulated climate change}
\end{center} 
\vspace{0.2cm}
\begin{center}
    \textit{Frontiers in Microbiology}\\
    \textit{DOI 10.3389/fmicb.2024.1319997}
\end{center}

@@

\begin{justify}
  Victoria Rodríguez\textsuperscript{1}, Alexander Bartholomäus\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Nicolás Riveras-Muñoz\textsuperscript{3}, Romulo Oses\textsuperscript{4}, Susanne Liebner\textsuperscript{1,5}, Jens Kallmeyer\textsuperscript{1}, Oliver Rach\textsuperscript{6}, Carsten W. Mueller\textsuperscript{7,8}, Oscar Seguel\textsuperscript{9}, Thomas Scholten\textsuperscript{3} and Dirk Wagner\textsuperscript{1,10}
\end{justify}

\vspace{0.2cm}

\begin{scriptsize}
  \begin{justify}
      \textsuperscript{1}GFZ German Research Centre for Geosciences, Section Geomicrobiology, Potsdam, Germany\\
      \textsuperscript{2}Soil Science, TUM School of Life Sciences, Technical University of Munich, Freising-Weihenstephan, Germany\\
      \textsuperscript{3}Department of Geosciences, Soil Science and Geomorphology, University of T{\"u}bingen, T{\"u}bingen, Germany\\
      \textsuperscript{4}Centro Regional de Investigaci{\'o}n y Desarrollo Sustentable de Atacama (CRIDESAT), Universidad de Atacama, Copiap{\'o}, Chile\\
      \textsuperscript{5}Institute of Biochemistry and Biology, University of Potsdam, Potsdam, Germany\\
      \textsuperscript{6}GFZ German Research Centre for Geosciences, Section Geomorphology, Potsdam, Germany\\
      \textsuperscript{7}Institute for Ecology, Chair of Soil Science, Technische Universit{\"a}t Berlin, Berlin, Germany\\
      \textsuperscript{8}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark\\
      \textsuperscript{9}Facultad de Ciencias Agron{\'o}micas, Universidad de Chile, Santiago, Chile\\
      \textsuperscript{10}Institute of Geosciences, University of Potsdam, Potsdam, Germany
  \end{justify}
\end{scriptsize}

\vspace{0.4cm}

\begin{flushleft}
    Received: 11 October 2023\\
    Accepted: 02 January 2024\\
    Published: 17 January 2024
\end{flushleft}

\cleardoublepage

@@

\bibliographystyle{natbib} % Consider changing to a style compatible with KOMA/natbib if issues arise
\bibliography{literatur_all_clean}

### 2025-04-06 tex/Manuscript-4.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.

\begin{center}
    \textbf{\Large Manuscript 4}

    \vspace{0.3cm}
    \textit{Geoderma}\\
    \textit{DOI 10.2139/ssrn.4740477}

    \vspace{0.5cm}

    Julia Mitzscherling\textsuperscript{1*}, Rómulo Oses\textsuperscript{2}, Nicolás Riveras-Muñoz\textsuperscript{3}, Carsten W. Müller\textsuperscript{4,5}, Oscar Seguel\textsuperscript{6},   Peter Kühn\textsuperscript{3}, Thomas Scholten\textsuperscript{3} and Dirk Wagner\textsuperscript{1,7}

    \vspace{0.2cm}
  \end{center}

@@

  \vspace{0.5cm}
  \begin{center}
    Received: 27 February 2024
  \end{center}
  \cleardoublepage

@@

Soil aggregation is highly correlated with soil moisture, clay and organic carbon content \citep{AlKaisi2014} and is one controlling factor of the dynamic and spatial variation in soil properties \citep{Totsche2018}. The moisture regime in soils is largely controlled by climate which in turn controls soil formation. This has been shown in great detail along the Coastal Cordillera of Chile \citep{Bernhard2018b}. Climatic factors such as precipitation and temperature affect soil biological, soil chemical and soil physical processes such as the accumulation or organic carbon, weathering of minerals and swelling and shrinking of clay particles as well as soil properties. Terrestrial ecosystems experience regular changes in water availability, a critical resource for life. Alternating wet-dry events significantly influence soil aggregate formation and stabilization processes \citep{Najera2020}.

@@

In the frame of the EarthShape project (German Science Foundation SPP 1803), soils were studied at the following four study sites distributed over \SI{1300}{\kilo\metre} along the Chilean Coastal Cordillera: Pan de Az{\'u}car National Park (\(\sim\)\ang{26}S), Santa Gracia Nature Reserve (\(\sim\)\ang{30}S), La Campana National Park (\(\sim\)\ang{33}S), and Nahuelbuta National Park (\(\sim\)\ang{38}S). 
The study sites cover a climate gradient with decreasing annual temperature and increasing annual precipitation from north to south and corresponded to arid, semi-arid, mediterranean and humid climates (\cref{fig:figure_1_label}) resulting in different soil moisture regimes \citep{Bernhard2018b}. 
Due to the long-term impact of stable climate conditions \citep{Ewing2006} soils show different stages of soil development. 
They were classified into Regosols in Pan de Az{\'u}car, Cambisols in Santa Gracia and La Campana, and Umbrisols in Nahuelbuta \citep{Bernhard2018b}. 
Vegetation types range from very sparse higher plant desert vegetation in the north, where biocrust soil coverage can reach as much as \SI{40}{\percent} of the area (biocrust-dominated desert vegetation) over semi-desert open shrubland and mediterranean dry forest and to temperate mixed broadleaved-coniferous forest in the south \citep{Bernhard2018a, Bernhard2018b}.

@@

\bibliographystyle{natbib}
\bibliography{literatur-M4}

>>>>

\begin{center}
  \textbf{\Large Manuscript 4}
\end{center}  
\vspace{0.1cm}
\begin{center}
  \textbf{\huge Microbially induced soil aggregate turnover across different climates and moisture regimes}

    \vspace{0.2cm}
    \textit{Geoderma}\\
    \textit{DOI 10.2139/ssrn.4740477}

    \vspace{0.1cm}

  \end{center}
  \begin{justify}
    Julia Mitzscherling\textsuperscript{1}, Rómulo Oses\textsuperscript{2}, Nicolás Riveras-Muñoz\textsuperscript{3}, Carsten W. Müller\textsuperscript{4,5}, Oscar Seguel\textsuperscript{6},   Peter Kühn\textsuperscript{3}, Thomas Scholten\textsuperscript{3} and Dirk Wagner\textsuperscript{1,7}
  \end{justify}

  \vspace{0.2cm}

@@

  \vspace{0.4cm}
  \begin{flushleft}
    Received: 27 February 2024
  \end{flushleft}
  \cleardoublepage

@@

Soil aggregation is highly correlated with soil moisture, clay and organic carbon content \citep{AlKaisi2014} and is one controlling factor of the dynamic and spatial variation in soil properties \citep{Totsche2018}. The moisture regime in soils is largely controlled by climate which in turn controls soil formation. This has been shown in great detail along the Coastal Cordillera of Chile \citep{Bernhard2018}. Climatic factors such as precipitation and temperature affect soil biological, soil chemical and soil physical processes such as the accumulation or organic carbon, weathering of minerals and swelling and shrinking of clay particles as well as soil properties. Terrestrial ecosystems experience regular changes in water availability, a critical resource for life. Alternating wet-dry events significantly influence soil aggregate formation and stabilization processes \citep{Najera2020}.

@@

In the frame of the EarthShape project (German Science Foundation SPP 1803), soils were studied at the following four study sites distributed over \SI{1300}{\kilo\metre} along the Chilean Coastal Cordillera: Pan de Az{\'u}car National Park (\(\sim\)\ang{26}S), Santa Gracia Nature Reserve (\(\sim\)\ang{30}S), La Campana National Park (\(\sim\)\ang{33}S), and Nahuelbuta National Park (\(\sim\)\ang{38}S). 
The study sites cover a climate gradient with decreasing annual temperature and increasing annual precipitation from north to south and corresponded to arid, semi-arid, mediterranean and humid climates (\cref{fig:figure_1_label}) resulting in different soil moisture regimes \citep{Bernhard2018}. 
Due to the long-term impact of stable climate conditions \citep{Ewing2006} soils show different stages of soil development. 
They were classified into Regosols in Pan de Az{\'u}car, Cambisols in Santa Gracia and La Campana, and Umbrisols in Nahuelbuta \citep{Bernhard2018b}. 
Vegetation types range from very sparse higher plant desert vegetation in the north, where biocrust soil coverage can reach as much as \SI{40}{\percent} of the area (biocrust-dominated desert vegetation) over semi-desert open shrubland and mediterranean dry forest and to temperate mixed broadleaved-coniferous forest in the south \citep{Bernhard2018a, Bernhard2018b}.

@@

\bibliographystyle{natbib} % Consider changing to a style compatible with KOMA/natbib if issues arise
\bibliography{literatur_all_clean}

### 2025-04-06 tex/Manuscript-5.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.

\begin{center}
    \textbf{\Large Manuscript 5}

    \vspace{0.3cm}
    \textit{Soil Biology and Biochemistry}\\
    \textit{DOI 10.1016/j.soilbio.2024.109503}

    \vspace{0.5cm}
    \begin{justify}
    Kristina Witzgall\textsuperscript{1}, Franziska Steiner\textsuperscript{1}, Benjamin D. Hesse\textsuperscript{2,3}, Nicolás Riveras-Muñoz\textsuperscript{4}, Victoria Rodríguez\textsuperscript{5}, Pedro Teixeira\textsuperscript{1}, Li, M.\textsuperscript{6}, Rómulo Oses\textsuperscript{7}, Oscar Seguel\textsuperscript{8}, Steffen Seitz\textsuperscript{4}, Dirk Wagner\textsuperscript{5,6}, Thomas Scholten\textsuperscript{4}, Franz Buegger\textsuperscript{9} Gerrit Angst\textsuperscript{7,11,12}, and Carsten W. Mueller\textsuperscript{1,13,14}
    \end{justify}
    \vspace{0.2cm}
  \end{center}

@@

  \vspace{0.5cm}
  \begin{center}
    Received: 27 February 2024\\
    Received: 13 November 2023\\ 
    Received in revised form: 15 June 2024\\
    Accepted: 17 June 2024\\
    Available online: 18 June 2024
  \end{center}
  \cleardoublepage

@@

\begin{description}
    \item[K. Witzgall:] Writing- review \& editing, Writing- original draft, Visualization, Methodology, Investigation, Formal analysis, Data curation, Conceptualization.
    \item[F.A. Steiner:] Writing- review \& editing, Writing- original draft, Investigation, Formal analysis, Data curation, Conceptualization.
    \item[B.D. Hesse:] Writing- review \& editing, Investigation, Data curation.
    \item[N. Riveras-Mu{\~n}oz:] Writing- review \& editing, Methodology, Data curation.
    \item[V. Rodr{\'\i}guez:] Writing- review \& editing, Methodology, Data curation. % Assuming accent on i
    \item[P.P.C. Teixeira:] Writing- review \& editing, Validation, Investigation.
    \item[M. Li:] Methodology.
    \item[R. Oses:] Writing- review \& editing, Conceptualization.
    \item[O. Seguel:] Writing- review \& editing, Conceptualization.
    \item[S. Seitz:] Writing- review \& editing, Conceptualization.
    \item[D. Wagner:] Writing- review \& editing, Supervision, Conceptualization.
    \item[T. Scholten:] Writing- review \& editing, Supervision, Resources, Funding acquisition, Conceptualization.
    \item[F. Buegger:] Writing- review \& editing, Formal analysis, Data curation.
    \item[G. Angst:] Writing- review \& editing, Supervision, Data curation, Conceptualization.
    \item[C.W. Mueller:] Writing- review \& editing, Validation, Supervision, Project administration, Methodology, Funding acquisition, Conceptualization.
\end{description}

@@

\bibliographystyle{natbib}
\bibliography{literatur-M5}

>>>>

\begin{center}
  \textbf{\Large Manuscript 5}
\end{center}  
\vspace{0.1cm}
\begin{center}
  \textbf{\huge Living and decaying roots as regulators of soil aggregation and organic matter formation---from the rhizosphere to the detritusphere}
\end{center}  
\vspace{0.2cm}
\begin{center}
  \textit{Soil Biology and Biochemistry}\\
  \textit{DOI 10.1016/j.soilbio.2024.109503}
\end{center}
\vspace{0.1cm}

\begin{justify}
    Kristina Witzgall\textsuperscript{1}, Franziska Steiner\textsuperscript{1}, Benjamin D. Hesse\textsuperscript{2,3}, Nicolás Riveras-Muñoz\textsuperscript{4}, Victoria Rodríguez\textsuperscript{5}, Pedro Teixeira\textsuperscript{1}, Li, M.\textsuperscript{6}, Rómulo Oses\textsuperscript{7}, Oscar Seguel\textsuperscript{8}, Steffen Seitz\textsuperscript{4}, Dirk Wagner\textsuperscript{5,6}, Thomas Scholten\textsuperscript{4}, Franz Buegger\textsuperscript{9} Gerrit Angst\textsuperscript{7,11,12}, and Carsten W. Mueller\textsuperscript{1,13,14}
\end{justify}

\vspace{0.2cm}

@@

\vspace{0.4cm}

\begin{flushleft}
    Received: 27 February 2024\\
    Received: 13 November 2023\\ 
    Received in revised form: 15 June 2024\\
    Accepted: 17 June 2024\\
    Available online: 18 June 2024
\end{flushleft}

\cleardoublepage

@@

    \textbf{K. Witzgall:} Writing- review \& editing, Writing- original draft, Visualization, Methodology, Investigation, Formal analysis, Data curation, Conceptualization.
    \textbf{F.A. Steiner:} Writing- review \& editing, Writing- original draft, Investigation, Formal analysis, Data curation, Conceptualization.
    \textbf{B.D. Hesse:} Writing- review \& editing, Investigation, Data curation.
    \textbf{N. Riveras-Mu{\~n}oz:} Writing- review \& editing, Methodology, Data curation.
    \textbf{V. Rodr{\'\i}guez:} Writing- review \& editing, Methodology, Data curation. % Assuming accent on i
    \textbf{P.P.C. Teixeira:} Writing- review \& editing, Validation, Investigation.
    \textbf{M. Li:} Methodology.
    \textbf{R. Oses:} Writing- review \& editing, Conceptualization.
    \textbf{O. Seguel:} Writing- review \& editing, Conceptualization.
    \textbf{S. Seitz:} Writing- review \& editing, Conceptualization.
    \textbf{D. Wagner:} Writing- review \& editing, Supervision, Conceptualization.
    \textbf{T. Scholten:} Writing- review \& editing, Supervision, Resources, Funding acquisition, Conceptualization.
    \textbf{F. Buegger:} Writing- review \& editing, Formal analysis, Data curation.
    \textbf{G. Angst:} Writing- review \& editing, Supervision, Data curation, Conceptualization.
    \textbf{C.W. Mueller:} Writing- review \& editing, Validation, Supervision, Project administration, Methodology, Funding acquisition, Conceptualization.

@@

\bibliographystyle{natbib} % Consider changing to a style compatible with KOMA/natbib if issues arise
\bibliography{literatur_all_clean}
